---
title: "Statistical Inference Project Part 2"
author: "Smriti Gambhir"
date: "February 28, 2016"
output:
  html_document: default
  pdf_document:
    latex_engine: miktex
---

**1. Load the ToothGrowth data and perform some basic exploratory data analyses.**

```{r}
data("ToothGrowth")
str(ToothGrowth)
```

```{r}
summary(ToothGrowth)
```

dose versus len and supp versus len plots
```{r}
par(mfrow=c(1,2))
plot(dose~len,data = ToothGrowth,pch=19)
plot(as.numeric(supp)~len,data = ToothGrowth,pch=19)
```

```{r}
par(mfrow=c(1,2))
boxplot(len~supp,data = ToothGrowth,col="red")
boxplot(len~dose,data = ToothGrowth,col="green")
```

**2.Perform some relevant confidence intervals and/or tests**

```{r}
t.test(len ~ supp, ToothGrowth[ToothGrowth$dose == .5, ])
```

```{r}
t.test(len ~ supp, ToothGrowth[ToothGrowth$dose == 1, ])
```

```{r}
t.test(len ~ supp, ToothGrowth[ToothGrowth$dose == 2, ])
```

**Conclusions**

Lower p-value for dose=0.5 and dose=1 indicates significant difference in means as can be seen [13.23-7.98=5.25 and 22.70-16.77=5.93]
Whereas higher p-value for dose=2 indicates a very small or insignificant difference in mean.
